
\section{E2017120501: Why xm2.org on XMark600 returns nothing?}

\subsection{Check With BaseX}
To find the reason, I used count() function tested the following 
queries, Q1--Q5 (Q1 is the original) over XMark600 using HaoLab.\\ 
\verb|Q1:/site//incategory[./@category="category52"]/parent::item/@id|\\
\verb|Q2:/site//incategory[./@category="category52"]|\\
\verb|Q3:/site//incategory[@category]|\\
\verb|Q4:/site//incategory[contains(@category, "52")]|\\
\verb|Q5:/site//incategory[contains(@category, "category52")]|\\

The results are listed as below:

\vspace{2mm}
\begin{tabular}{c|c|c|c|c|c}
	\hline
	query & count(Q1) & count(Q2) & count(Q3) & count(Q4) & count(Q5) \\
	\hline
	result & 0        &      0    & 49,514,754& 2,720,824 & 895,154 \\
	\hline
\end{tabular}
\vspace{2mm}

We then outputted the results of Q4 and Q5. After checking the 
results, there was no node that matchs "category52" found.
The nodes found were \texttt{interest} nodes that have the contents 
started with  \texttt{category52} such as 

\verb|<incategory category="category526763"/>|. 

\subsection{Check Without BaseX}
From the above results, it is clear that no "incategory" node has 
an attribute with content of "category52". To make sure this 
conclusion, we did another test without using BaseX.

The test is to find string \verb|category="category52"| by reading 
and comparing each line in the xmark600.xml. The java code is listed
as below: 

\begin{lstlisting}[language=java,frame=single]
public static void main(String[] args) throws Exception {
    FileReader reader = new FileReader(args[0]);
    BufferedReader br = new BufferedReader(reader);
    String str = null;
    int lineno = 0;
    while ((str = br.readLine()) != null) {
        lineno++;
        if (str.contains(args[1]))
            System.out.println("Found in line " +
              lineno + ": " + str);
    }
    br.close();
    reader.close();
}
\end{lstlisting}

We executed it by the following command.\\
\verb|java -cp test.jar basex.Finder xmark600.xml category=\"category52\"|

Then, what we found are listed as below.\\
\verb|Found in line 424449141: <interest category="category52"/>|\\
\verb|...|\\
\verb|Found in line 658701472: <interest category="category52"/>|\\
(The full results are stored in the file ``\texttt{experiments/E2017120501/results.txt}"). 

There is no \texttt{incategory} node in xmark600 found with attribute category="category52". 

Therefore, the results of xm2.org E2017120401 in report are correct.


